### 2023-03-23 intro.tex
Updates from Overleaf

Local type inference pairs well with type error localization and recovery because information flows systematically through the tree, leading to predictable and systematic localization decisions (as informally observed also by \cite{LocalInf}). Languages with constraint-based type inference gather constraints from all relevant locations in a program. This approach is powerful, but it is also notorious for complicating type error localization and recovery, because inconsistencies can arise through a confluence of constraints originating from any number of locations in the program.

>>>>

Local type inference pairs well with type error localization and recovery because information flows systematically through the tree, leading to predictable and systematic localization decisions (as informally observed also by \cite{Localinf}). Languages with constraint-based type inference gather constraints from all relevant locations in a program. This approach is powerful, but it is also notorious for complicating type error localization and recovery, because inconsistencies can arise through a confluence of constraints originating from any number of locations in the program.
